SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2018-10-05 scipy-1.0/paper.tex
Spellcheck

Therefore, the relative abundance of different programming languages in the
SciPy library results from a combination of the usage of powerful performance
enhancing languages that interact well with Python (i.e., Cython), and the
usage of languages (and their libraries) that have proven reliable and
performant over many decades. The position that SciPy occupies near the
foundation of the scientific Python ecosystem is such that adoption of new
languages or major dependencies is generally unlikely--our choices are strongly
driven by long-term stability. GPU acceleration, new transpiling libraries, and
the latest JIT compilation approaches (i.e.,
Numba\cite{Lam:2015:NLP:2833157.2833162}) are very powerful, but currently fall
outside the remit of the main SciPy library. That said, we have recently
increased our efforts to support compatibility with some of these options, and
having our full test suite pass with the PyPy JIT
compiler\cite{Bolz:2009:TMP:1565824.1565827} is now a requirement in our
development workflow.

@@

The (currently) 18 member Steering Council is chaired by Ralf Gommers and
performs a number of tasks including nominating and voting on new Council
Members, and actively contributing to the progress of the project (could be
code review but also outreach activities, etc.). Generally, 1 year of sustained
and substantial contributions (not restricted to source code contributions)
that improve the project are the prerequisites for nomination of new Council
Members. Council Members do not get special treatment for the vast majority of
the day to day project activities (code submission / review), though it is
anticipated that their experience with the project will serve as helpful
guidance in many matters.  Council Members have commit rights to the project,
but will typically only incorporate changes when there are no substantive
community objections. The Chair of the Steering Council is responsible for
starting more formal technical reviews of the direction of the project,
ensuring that the composition of the Council remains current, and communicating
/ summarizing any Council activities performed privately to the broader
community. We also describe in some detail how institutional partners may
contribute to the project, but no financial weight from grants or other sources
may be leveraged to circumvent or overrule the technical direction of the
project decided upon by the Steering Committee. The Chair does not have a fixed
term, but is nominated by the Steering Committee and is expected to yield to
substantive claims that stepping down is the appropriate action.

@@

The SciPy project has approximately 15 active maintainers - people who review
others' contributions, and in general do everything needed to ensure that the
software and the project move forward. Maintainers are critical to the health
of the project\cite{eghbal2016}; their skills and efforts largely determine how
fast the project moves forward, and they enable contributions from a much
larger group. Accordingly, the project also has an additional ~100 unique
contributors for every 6-monthly release cycle. Anyone with the interest and
skills can become a contributor or maintainer; the SciPy Developer Guide
provides guidance on how to do that.

>>>>

Therefore, the relative abundance of different programming languages in the
SciPy library results from a combination of the usage of powerful performance
enhancing languages that interact well with Python (i.e., Cython), and the
usage of languages (and their libraries) that have proven reliable and
performant over many decades. The position that SciPy occupies near the
foundation of the scientific Python ecosystem is such that adoption of new
languages or major dependencies is generally unlikely---our choices are strongly
driven by long-term stability. GPU acceleration, new transpiling libraries, and
the latest JIT compilation approaches (i.e.,
Numba\cite{Lam:2015:NLP:2833157.2833162}) are very powerful, but currently fall
outside the remit of the main SciPy library. That said, we have recently
increased our efforts to support compatibility with some of these options, and
having our full test suite pass with the PyPy JIT
compiler\cite{Bolz:2009:TMP:1565824.1565827} is now a requirement in our
development workflow.

@@

The (currently) 18 member Steering Council is chaired by Ralf Gommers and
performs a number of tasks including nominating and voting on new Council
Members, and actively contributing to the progress of the project (could be
code review but also outreach activities, etc.). Generally, one year of sustained
and substantial contributions (not restricted to source code contributions)
that improve the project are the prerequisites for nomination of new Council
Members. Council Members do not get special treatment for the vast majority of
the day to day project activities (code submission / review), though it is
anticipated that their experience with the project will serve as helpful
guidance in many matters.  Council Members have commit rights to the project,
but will typically only incorporate changes when there are no substantive
community objections. The Chair of the Steering Council is responsible for
starting more formal technical reviews of the direction of the project,
ensuring that the composition of the Council remains current, and communicating
/ summarizing any Council activities performed privately to the broader
community. We also describe in some detail how institutional partners may
contribute to the project, but no financial weight from grants or other sources
may be leveraged to circumvent or overrule the technical direction of the
project decided upon by the Steering Committee. The Chair does not have a fixed
term, but is nominated by the Steering Committee and is expected to yield to
substantive claims that stepping down is the appropriate action.

@@

The SciPy project has approximately 15 active maintainers---people who review
others' contributions, and in general do everything needed to ensure that the
software and the project move forward. Maintainers are critical to the health
of the project\cite{eghbal2016}; their skills and efforts largely determine how
fast the project moves forward, and they enable contributions from a much
larger group. Accordingly, the project also has an additional ~100 unique
contributors for every 6-monthly release cycle. Anyone with the interest and
skills can become a contributor or maintainer; the SciPy Developer Guide
provides guidance on how to do that.

### 2018-10-05 scipy-1.0/scipy-optimize.tex
Spellcheck

A new interior-point optimizer for continuous linear programming problems, \texttt{linprog} with \texttt{method='interior-point'}, was released with SciPy 1.0. Implementing the core algorithm of the commercial solver MOSEK \cite{andersen2000mosek}, it solves all of the 90+ NETLIB LP benchmark problems \cite{netlib} tested. Unlike some interior point methods, this homogenous self-dual formulation provides certificates of infeasibility or unboundedness as appropriate.

A presolve routine \cite{andersen1995presolving} solves trivial problems and otherwise performs problem simplifications, such as bound tightening and removal of fixed variables, and one of several routines for eliminating redundant equality constraints is automatically chosen to reduce the chance of numerical difficulties caused by singular matrices. Although the main solver implementation is pure Python, end-to-end sparse matrix support and heavy use of SciPy's compiled linear system solvers --- often for the same system with multiple right hand sides due to the predictor-corrector approach --- provide speed sufficient for problems with tens of thousands of variables and constraints.

>>>>

A new interior-point optimizer for continuous linear programming problems, \texttt{linprog} with \texttt{method='interior-point'}, was released with SciPy 1.0. Implementing the core algorithm of the commercial solver MOSEK \cite{andersen2000mosek}, it solves all of the 90+ NETLIB LP benchmark problems \cite{netlib} tested. Unlike some interior point methods, this homogeneous self-dual formulation provides certificates of infeasibility or unboundedness as appropriate.

A presolve routine \cite{andersen1995presolving} solves trivial problems and otherwise performs problem simplifications, such as bound tightening and removal of fixed variables, and one of several routines for eliminating redundant equality constraints is automatically chosen to reduce the chance of numerical difficulties caused by singular matrices. Although the main solver implementation is pure Python, end-to-end sparse matrix support and heavy use of SciPy's compiled linear system solvers---often for the same system with multiple right hand sides due to the predictor-corrector approach---provide speed sufficient for problems with tens of thousands of variables and constraints.
